% !TEX root = ../main.tex
\section{Classes}

% --- Simple full-width class card (no extra packages) ---
\newcommand{\ClassCard}[4]{%
  \noindent\fbox{%
    \parbox[t]{\linewidth}{%
      \textbf{#1}\par
      \small
      \textbf{Dice Gain per Level:} #2\par
      \textbf{Concept.} #3\par
      \textbf{Playstyle.} #4%
    }%
  }\par\vspace{5mm}%
}

% ===== RED DICERS — Strength, Fury, Presence =====
\subsection*{Red Dicers — Strength, Fury, Presence}

\ClassCard
  {Berserker}
  {+2 Red}
  {Pure rage and relentless assault.}
  {Unchecked physical offense; thrives in chaos and extended melees.}

\ClassCard
  {Warrior}
  {+1 Red, +1 Blue}
  {Disciplined master of combat.}
  {Balances attack and defense; stays effective in any phase of battle.}

\ClassCard
  {Warlord}
  {+1 Red, +1 Yellow}
  {Commander of the front line.}
  {Inspires allies; can share setup or rerolls through tactical shouts.}

\ClassCard
  {Pyrowarrior}
  {+1 Red, +1 Purple}
  {Fire-infused fighter (Red + Pyro).}
  {Empowers weapons with flame; excels at damage over time and pressure.}

\ClassCard
  {Stormblade}
  {+1 Red, +1 Purple}
  {Elemental warrior (Red + Lightning).}
  {Channels volatile energy into explosive strikes and burst repositioning.}

\clearpage

% ===== BLUE DICERS — Defense, Endurance, Control =====
\subsection*{Blue Dicers — Defense, Endurance, Control}

\ClassCard
  {Defender}
  {+2 Blue}
  {The unbreakable wall.}
  {Absorbs or redirects hits; shields allies and anchors objectives.}

\ClassCard
  {Sentinel}
  {+1 Blue, +1 Yellow}
  {Battlefield controller.}
  {Interrupts and punishes overreach; reactive counters and zones.}

\ClassCard
  {Roller}
  {+1 Blue, +1 Purple}
  {Shield mage (Blue + Earth).}
  {Shapes stone and terrain to deflect and fortify; excels at chokepoints.}

\ClassCard
  {Drencher}
  {+1 Blue, +1 Purple}
  {Water-tuned protector (Blue + Water).}
  {Flows between liquid defense and frozen retaliation; flexible mitigation.}

\ClassCard
  {Mender}
  {+1 Blue, +1 Purple}
  {Healer (Blue + Verdant).}
  {Restores wounds and stabilizes allies; master of recovery and sustain.}

\ClassCard
  {Arbiter}
  {+1 Blue, +1 Purple}
  {Enforcer of Order (Order magic).}
  {Reduces chaos, imposes structure, and defines battlefield constraints.}

\clearpage

% ===== YELLOW DICERS — Agility, Precision, Adaptability =====
\subsection*{Yellow Dicers — Agility, Precision, Adaptability}

\ClassCard
  {Rogue}
  {+2 Yellow}
  {Quick and cunning skirmisher.}
  {Nimble attacks, constant dodges, and advantage manipulation.}

\ClassCard
  {Ranger}
  {+1 Yellow, +1 Blue}
  {Expert hunter.}
  {Pursuit, survival, and precision ranged engagements.}

\ClassCard
  {Sniper}
  {+1 Yellow, +1 Red}
  {Long-ranged fighter (Yellow + Red).}
  {Converts patience and focus into sudden, lethal bursts from afar.}

\ClassCard
  {Dragoon}
  {+1 Yellow, +1 Purple}
  {Air-infused duelist (Yellow + Air).}
  {Wind-aided leaps, speed, and mid-air strikes; thrives on verticality.}

\ClassCard
  {Illuminar}
  {+1 Yellow, +1 Purple}
  {Mirror magic empath.}
  {Reflects opponents, distorts identity and perception; counters single targets.}

\ClassCard
  {Thantom}
  {+1 Yellow, +1 Purple}
  {Decay channeler (Yellow + Thano).}
  {Manipulates corrosion and entropy to slow foes and obscure self.}

\clearpage

% ===== PURPLE DICERS — Magic, Flow, Transformation =====
\subsection*{Purple Dicers — Magic, Flow, Transformation}

\ClassCard
  {Magademic}
  {+1 Purple}
  {Scholar of the arcane.}
  {Masters rote patterns; casts from memory with dependable cadence.}

% Mancer — presented as a wide block with focus options
\noindent\fbox{%
  \parbox[t]{\linewidth}{%
    \textbf{Mancer (Elemental magic)}\par
    \small
    \textbf{Dice Gain per Level:} +1 Purple (occasional Elemental die)\par
    \textbf{Concept.} Master of a single elemental path.\par
    \textbf{Focus options.}
    \begin{itemize}
      \item \textbf{Pyromancer} — Fire \& fury (Red synergy).
      \item \textbf{Aeromancer} — Wind \& agility (Yellow synergy).
      \item \textbf{Hydromancer} — Water \& adaptability (Blue synergy).
      \item \textbf{Electromancer} — Lightning \& speed (often Red synergy).
      \item \textbf{Geomancer} — Earth \& endurance (Blue synergy).
      \item \textbf{Biomancer} — Verdant life \& growth (Blue synergy).
      \item \textbf{Thanomancer} — Decay \& corrosion (Yellow synergy).
    \end{itemize}
  }%
}\par\vspace{5mm}

\ClassCard
  {Chronomancer}
  {+1 Purple (occasional Yellow)}
  {Weaver of time (Time magic).}
  {Alters sequence and tempo to reshape outcomes; excels at initiative control.}

\ClassCard
  {Witherer}
  {+1 Purple (occasional Blue)}
  {Somatic shaper of vitality (Life magic).}
  {Outlawed practice manipulating life force; heals or drains with equal pace.}

\ClassCard
  {Dream Weaver}
  {+1 Purple (occasional wild dice)}
  {Bridge to the liminal (Dream magic).}
  {Bends reality toward dreams, shaping illusion and possibility across the field.}
