\section{Character Creation}

\noindent
Every hero begins as potential — a balance of daring, skill, and chance.
Follow these steps to shape a new character.

\subsection*{1. Choose Your Core Stats}

Each character has six attributes:

\begin{itemize}
  \item \textbf{Brawn (Red Dice):} Physical strength, determination, and raw force.
  \item \textbf{Grit (Blue Dice):} Defence, endurance, and the ability to hold ground.
  \item \textbf{Vim (Yellow Dice):} Agility, reflexes, and quick-thinking flair.
  \item \textbf{Moxie (Social/Trinity Influence):} Presence, nerve, and emotional drive.  Moxie upgrades the Trinity Dice during social or narrative conflicts.
  \item \textbf{Cognition (Purple Dice):} Intellect, arcane understanding, and creativity.
  \item \textbf{Fortune or Resolve (Choice):}  
        Roll \texttt{3d6}.  
        \textbf{Fortune} governs luck, coincidence, and fate’s favour.  
        \textbf{Resolve} measures willpower, tenacity, and resistance to despair.
\end{itemize}

All attributes start at~10.  
Choose one attribute to reduce to~8, and raise three others by~2 each.  
This creates a distinct silhouette — one weakness and three defining strengths.

\subsection*{2. Choose a Race}

Your race determines certain natural aptitudes, instincts, and limitations.
It may modify your stats, alter recovery rates, or unlock unique dice interactions.

\subsection*{3. Choose a Background}

Your background defines who you were before adventure found you.
It grants narrative skills, starting gear, and role-playing hooks.

\subsection*{4. Choose a Vocation}

Your vocation — also called your \textbf{class} — determines your dice progression,
combat style, and role within the group.
Each vocation has its own dice colour focus and growth pattern.

\subsection*{5. Record Your Starting Dice Pool}

Start with the dice appropriate to your vocation and adjusted by your stats.
You’ll add or upgrade dice as you advance.

\medskip
\noindent
\textit{Example:}
A character with Grit~12, Guard~10, Dash~8, Moxie~12, Wit~10, and Fortune~11
chooses the \textbf{Warlord} vocation.
Their strong Grit and Moxie grant extra red dice for aggression and leadership,
while low Dash makes them slower to react — a commander, not a duelist.
